---
  output: github_document
---

[![Travis build status](https://travis-ci.com/muschellij2/biostatmethods.svg?branch=master)](https://travis-ci.com/muschellij2/biostatmethods)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/muschellij2/biostatmethods?branch=master&svg=true)](https://ci.appveyor.com/project/muschellij2/biostatmethods)
[![Coverage status](https://coveralls.io/repos/github/muschellij2/biostatmethods/badge.svg?branch=master)](https://coveralls.io/r/muschellij2/biostatmethods?branch=master)
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```
# biostatmethods Package: 
The goal of `biostatmethods` is to provide accompanying code and data from the book ["Methods in Biostatistics with R"](https://leanpub.com/biostatmethods).

## Accessing the Data

All the data from the book is located in the `inst/extdata` folders.  If you would like to download these, they can be accessed from http://johnmuschelli.com/.  For example:

http://johnmuschelli.com/biostatmethods/inst/extdata/bmi_age.txt
http://johnmuschelli.com/biostatmethods/inst/extdata/NIfTI/FLAIR.nii.gz

should be links that will download the data (if you click Save As).

### Accessing the Sleep Heart Health Study Data

The `shhs1.txt` file is from the Sleep Heart Health Study (https://sleepdata.org/datasets/shhs).  

To obtain access to the SHHS data, please visit the National Sleep Research Resource (NSRR) at https://sleepdata.org/datasets/shhs.  When completing the NSRR data access request to obtain the `shhs1.txt` data file, please use the following information in the Title and Specific Purpose fields of the online application:
```
Title:  Methods in Biostatistics with R

Specific Purpose: Requesting access to the SHHS dataset to complete the exercises in the "Methods in Biostatistics with R" textbook, and I understand that I cannot share the data with others or make the data available via any other means per the terms of the NSRR Data Access and Use Agreement.
```

You should be able to download the file from the website.  Alternatively, once you've obtained access, grab your token from https://sleepdata.org/token, then you can download the `shhs1.txt` file by running:

```{r, eval = FALSE}
biostatmethods::biostat_download_shhs()
```

By default, `biostat_download_shhs` will download the file to where `biostatmethods` was installed but you can set an output directory with the `out_dir` argument.


## Data Inside the Package

If you want to access the data from the book, there is a simple function `biostat_data` that will return the filenames of these files.

```r
library(biostatmethods)
biostat_data("bmi_age.txt")
biostat_data("FLAIR.nii.gz")
```

One of the reasons that we included these as files rather than attached them into the package is that we believe data importing is one of the most important parts of data analysis and would like readers to get comfortable with that, whether it be a text file or a brain image.

## Installation

You can install `biostatmethods` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("muschellij2/biostatmethods")
```
